Effects of bulk gas rotation on the emergent Lyman-$\alpha$ line in distant galaxies

### 2013-02-20 paper/Analisis.tex
heavy reformatting

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Template for a LaTex article in English.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

%\usepackage[latin1]{inputenc}

\usepackage[english]{babel}
% AMS packages:
\usepackage{amsmath, amsthm, amsfonts, graphicx, float, caption, subfigure}

% Theorems
%-----------------------------------------------------------------
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}

% Shortcuts.
% One can define new commands to shorten frequently used
% constructions. As an example, this defines the R and Z used
% for the real and integer numbers.
%-----------------------------------------------------------------
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}

% Similarly, one can define commands that take arguments. In this
% example we define a command for the absolute value.
% -----------------------------------------------------------------
\newcommand{\abs}[1]{\left\vert#1\right\vert}

% Operators
% New operators must defined as such to have them typeset
% correctly. As an example we define the Jacobian:
% -----------------------------------------------------------------
\DeclareMathOperator{\Jac}{Jac}

%---------------------------------------------------------------

@@

@@

\section{Implementation of Rotation in CLARA}

We implement into CLARA the simplest model whereby a sphere rotates
with homogeneous angular velocity. We define a cartesian coordinate
system with its origin at the center of the sphere and the rotation
axis to be the $z$-axis, the velocity field in the gas can be written as

@@

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}V_{\max} \label{subeq1}\\
    v_{y}=\dfrac{x}{R}V_{\max} \label{subeq2}
\end{align}
\end{subequations}

Where $x$ and $y$ define de position of the gas atoms and dust
particles. The minus sign in the x-component of the velocity is due to
the direction of rotation, in this case we assume that as seeing from
the top,the rotation is anticlockwise.

\section{Simulated Models in CLARA}
\label{sec:models}

@@

\begin{figure}[H]

  \centering

  \label{HOMandCentral}\caption{Shape of the lyman alpha line for
    differents velocities. The left panel show the central
    distribution while the right panel show the homogeneous
    distribution. }

  \begin{tabular}{cc}    
    \includegraphics[width=60mm]{7tDifSpeedsZ.png}&
    \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\
  \end{tabular}

\end{figure}
Now if we take into account the position of the observer and compute
this for differents angles of observation $\theta$ the outcoming
spectra is modified as is shown in figure[2]. The main feature here is
that as the angle increases the line high decreases. It means that a
observer in the poles will observe a higher double peak than a
observer in the ecuator. We will understand this in more details when
we present the resaults of the scape fraction in section[].

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.45]{Observers.png}
\end{center}
\caption{Spectra for different observers. Model:$V=300km/s$, Optical
  Depth $\tau=10^{7}$ and Central Distribution without dust.} 
\end{figure}

@@

\section*{Resaults and Discussion}
\label{sec:Results_ly_Rotation}

@@

\subsection*{Maximums Position}

\begin{figure}[H]

  \centering

  \label{figur}\caption{Width of the lyman-alpha line for all the models. }

  \begin{tabular}{cc}

    \includegraphics[width=40mm]{0maximum7t.png}&

    \includegraphics[width=40mm]{0maximum6t.png}

    \includegraphics[width=40mm]{0maximum5t.png}

   \end{tabular}

\end{figure}
(comparar con la grafica del apendice de clara con el eje x el optical
depth y en el eje-y los maximos)

@@

\subsection*{Line Width}

@@

\begin{figure}[H]

  \centering

  \label{figur}\caption{Width of the lyman-alpha line for all the models. }

  \begin{tabular}{cc}

    \includegraphics[width=60mm]{WidthCentral.png}&

    \includegraphics[width=60mm]{WidthHomogeneous.png}\\

    \includegraphics[width=60mm]{Width6.png}&

    \includegraphics[width=60mm]{Width6HOM.png}\\

    \includegraphics[width=60mm]{Width5.png}&

    \includegraphics[width=60mm]{Width5HOM.png}\\

  \end{tabular}

\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.45]{WidthvsTheta.png}
\caption{Width variation in function of theta}
\end{center}
\end{figure}

\subsection*{Escape Fraction}

@@

\begin{figure}[H]

  \centering

  \label{figur}\caption{Escape fraction for all the models. Left
    panels show the central distribution, while right panels show the
    homogeneous distribution}

  \begin{tabular}{cc}

    \includegraphics[width=60mm]{FECentral5.png}&

    \includegraphics[width=60mm]{FEHOM5.png}\\

    \includegraphics[width=60mm]{FECentral6.png}&

    \includegraphics[width=60mm]{FEHOM6.png}\\

    \includegraphics[width=60mm]{FECentral7.png}&

    \includegraphics[width=60mm]{FEHOM7.png}\\

  \end{tabular}

\end{figure}

@@

\section*{Observational effect.}

\section*{Tables}

Maximos\\

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline          
Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ 
\hline 
50 & -16.2695 & 16.23705 \\ 
\hline 
100 & -15.66496 & 15.33504 \\ 
\hline 
200 & -16.93149 & 14.56851 \\ 
\hline 
300 & -13.40048 & 16.09952 \\ 
\hline 
\end{tabular} 
\caption{Optical Depth $\tau= 10^{7}$, Central Distribution}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity (Km/s) & Maximum 1 position & Maximum 2 position\\ 
\hline 
50 & -7.46286 & 6.53714 \\ 
\hline 
100 & -7.53357 & 6.96643 \\ 
\hline 
200 & -8.17453 & 7.32547 \\ 
\hline 
300 & -6.81487 & 6.18513 \\ 
\hline 
\end{tabular} 
\end{center}
\caption{Optical Depth $\tau = 10^{6}$, Central Distribution}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ 
\hline 
50 & -4.33708 & 3.66292 \\ 
\hline 
100 & -4.27326 & 3.72674 \\ 
\hline 
200 & -3.7737 & 3.7263   \\ 
\hline 
300 & -3.84903 & 4.15097 \\ 
\hline 
\end{tabular}
\caption{Optical Depth $\tau=10^{5}$, Central distribution} 
\end{center}
\end{table}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity(Km/s) & FWHM & $\theta$\\ 
\hline 
50 & 12.62 & $0^{o}$ \\ 
\hline 
50 & 12.72 & $45^{o}$ \\ 
\hline 
50 & 12.93 & $90^{o}$ \\ 
\hline 
100 & 14.07 & $0^{o}$ \\ 
\hline
100 & 14.48 & $45^{o}$ \\ 
\hline 
100 & 15.00 & $90^{o}$ \\ 
\hline 
200 & 16.90 & $0^{o}$  \\ 
\hline 
200 & 18.51 & $45^{o}$ \\ 
\hline 
200 & 21.24 & $90^{o}$ \\ 
\hline 
300 & $24.69^{*}$ & $0^{o}$ \\ 
\hline 
300 & $25.79^{*}$ & $45^{o}$  \\ 
\hline  
300 & $27.73^{*}$ & $90^{o}$ \\ 
\hline  
\end{tabular}
\caption{Lines Widhts for a Central Distribution and $\tau=10^{7}$} 
\end{center}
\end{table}

Scape fracton\\

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ 
\hline 
Homogeneous & 50 & $0^{o}$& 13293.06 &49939.53\\ 
\hline 
Homogeneous & 50 & $45^{o}$& 13291.04 &50001.59\\ 
\hline 
Homogeneous & 50 & $90^{o}$ & 13348.76 &49922.73\\ 
\hline 
Homogeneous & 100 & $0^{o}$ & 15527.69 &50114.11\\ 
\hline
Homogeneous & 100 & $45^{o}$ & 15511.56 &49967.17\\ 
\hline
Homogeneous & 100 & $90^{o}$ & 15401.71 & 49833.65\\ 
\hline 
Homogeneous & 200 & $0^{o}$  & 17830.85 & 50078.69\\ 
\hline 
Homogeneous & 200 & $45^{o}$ & 17932.87 & 50064.42\\ 
\hline 
Homogeneous & 200 & $90^{o}$ & 17830.85  & 49931.748\\ 
\hline
Homogeneous & 300 & $ 0^{o}$ & 18687.33 & 50048.33 \\ 
\hline 
Homogeneous & 300 & $45^{o}$ & 18572.12& 49922.67\\ 
\hline  
Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ 
\hline  
\end{tabular}
\caption{Escape fraction for a Homogeneous Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\ 
\hline 
Central & 50 & $0^{o}$ & 4809.881 & 49917.069 \\ 
\hline 
Central & 50 & $45^{o}$ & 4829.21 & 49811.79 \\ 
\hline 
Central & 50 & $90^{o}$ & 4845.108 & 49853.039\\ 
\hline 
Central & 100 & $0^{o}$ & 4809.665 & 49921.30 \\  
\hline
Central & 100 & $45^{o}$ & 4828.65 & 49820.13 \\ 
\hline
Central & 100 & $90^{o}$ & 4846.45 & 49854.0 \\ 
\hline 
Central & 200 & $0^{o}$  & 4809.63 & 49917.64 \\ 
\hline 
Central & 200 & $45^{o}$ & 4829.25 & 49818.49 \\ 
\hline 
Central & 200 & $90^{o}$ & 4844.89 & 49856.66 \\ 
\hline 
Central & 300 & $ 0^{o}$ & 4810.56 & 49922.98\\ 
\hline 
Central & 300 & $45^{o}$ & 4831.16 & 49823.33\\ 
\hline  
Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ 
\hline  
\end{tabular}
\caption{Escape fraction for the central Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}

>>>>

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig}  
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

\usepackage[normalem]{ulem}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}

% definition to produce a "less than or similar to" symbol
\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}

% definition to produce a "greater than or similar to" symbol
\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}

@@

\title[Rotation in the Lyman-$\alpha$ line]{Effects of bulk gas rotation on
  the emergent Lyman-$\alpha$ line in distant galaxies}
\author[N. Garavito and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Nicolas Garavito.$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

\begin{abstract}

\end{abstract}
\begin{keywords}
galaxies: high-redshift - galaxies: star formation - line: formation
\end{keywords}

@@

\section{Implementation of Bulk Gas Rotation}

We implement into CLARA the simplest model whereby a sphere rotates
with homogeneous angular velocity. We define a cartesian coordinate
system with its origin at the center of the sphere and the rotation
axis to be the $z$-axis, the components in the bulk velocity field, $\vec{v}
= v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{z}$. in the gas can be written as

@@

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}V_{\rm max}, \label{subeq1}\\
    v_{y}=\dfrac{x}{R}V_{\rm max}, \label{subeq2}\\
    v_{z}=0, \label{subeq3}
\end{align}
\end{subequations}

%Where $x$ and $y$ define de position of the gas atoms and dust
%particles. 
%The minus sign in the x-component of the velocity is due to
%the direction of rotation, in this case we assume that as seeing from
%the top,the rotation is anticlockwise.
where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus sign in the x-component of the velocity is due to
the direction of rotation, in this case we assume that the angular
velocity vector goes in the $\hat{k}$ direction.

\section{Grid of Simulated Models}
\label{sec:models}

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{7tDifSpeedsZ.png}
  \includegraphics[width=0.45\textwidth]{7tHOMDifSpeeds1.png}
  \label{fig:HOMandCentral}\caption{Shape of the lyman alpha line for
    differents velocities. The left panel show the central
    distribution while the right panel show the homogeneous
    distribution.}
\end{figure*}

Now if we take into account the position of the observer and compute
this for differents angles of observation $\theta$ the outcoming
spectra is modified as is shown in figure[2]. The main feature here is
that as the angle increases the line high decreases. It means that a
observer in the poles will observe a higher double peak than a
observer in the ecuator. We will understand this in more details when
we present the resaults of the scape fraction in section[].

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Observers.png}
\end{center}
\caption{Spectra for different observers. Model:$V=300km/s$, Optical
  Depth $\tau=10^{7}$ and Central Distribution without dust.} 
\end{figure}

@@

\section{Results}
\label{sec:Results}

@@

\subsection{Maximums Position}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{0maximum7t.png}
    \includegraphics[width=0.45\textwidth]{0maximum6t.png}
    \includegraphics[width=0.45\textwidth]{0maximum5t.png}
  \label{figure:maxima}\caption{Width of the lyman-alpha line for all the models. }
\end{figure}
(comparar con la grafica del apendice de clara con el eje x el optical
depth y en el eje-y los maximos)

@@

\subsection{Line Width}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
    \includegraphics[width=0.45\textwidth]{Width6.png}
    \includegraphics[width=0.45\textwidth]{Width6HOM.png}
    \includegraphics[width=0.45\textwidth]{Width5.png}
    \includegraphics[width=0.45\textwidth]{Width5HOM.png}
  \label{figure:width}\caption{Width of the lyman-alpha line for all the models. }
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
\caption{Width variation in function of theta}
\end{center}
\end{figure}

\subsection{Escape Fraction}

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FECentral5.png}
  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
  \includegraphics[width=0.45\textwidth]{FECentral6.png}
  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
  \includegraphics[width=0.45\textwidth]{FECentral7.png}
  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
  \label{figure:escape}\caption{Escape fraction for all the models. Left
    panels show the central distribution, while right panels show the
    homogeneous distribution} 
\end{figure*}

@@

\section{Discussion}
\label{sec:discussion}

\section{Observational implications}

\section{Conclusions}

\section*{Acknowledgements}

\section*{Appendix A: Tables}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline          
Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ \hline
50 & -16.2695 & 16.23705 \\ 
100 & -15.66496 & 15.33504 \\ 
200 & -16.93149 & 14.56851 \\ 
300 & -13.40048 & 16.09952 \\ \hline 
\end{tabular} 
\caption{Optical Depth $\tau= 10^{7}$, Central Distribution}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline 
Velocity (km/s) & Maximum 1 position & Maximum 2 position\\ \hline
50 & -7.46286 & 6.53714 \\ 
100 & -7.53357 & 6.96643 \\ 
200 & -8.17453 & 7.32547 \\ 
300 & -6.81487 & 6.18513 \\ \hline 
\end{tabular} 
\end{center}
\caption{Optical Depth $\tau = 10^{6}$, Central Distribution}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline 
Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ \hline
50 & -4.33708 & 3.66292 \\ 
100 & -4.27326 & 3.72674 \\ 
200 & -3.7737 & 3.7263   \\ 
300 & -3.84903 & 4.15097 \\ \hline 
\end{tabular}
\caption{Optical Depth $\tau=10^{5}$, Central distribution} 
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline 
Velocity(Km/s) & FWHM & $\theta$\\ \hline 
50 & 12.62 & $0^{o}$ \\ 
50 & 12.72 & $45^{o}$ \\ 
50 & 12.93 & $90^{o}$ \\ 
100 & 14.07 & $0^{o}$ \\ 
100 & 14.48 & $45^{o}$ \\ 
100 & 15.00 & $90^{o}$ \\ 
200 & 16.90 & $0^{o}$  \\ 
200 & 18.51 & $45^{o}$ \\ 
200 & 21.24 & $90^{o}$ \\ 
300 & $24.69^{*}$ & $0^{o}$ \\ 
300 & $25.79^{*}$ & $45^{o}$  \\ 
300 & $27.73^{*}$ & $90^{o}$ \\ \hline
\end{tabular}
\caption{Lines Widhts for a Central Distribution and $\tau=10^{7}$} 
\end{center}
\end{table}

Escape fraction\\

\begin{table}[H]
\begin{center}
\begin{tabular}{ccccc}\hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ \hline 
Homogeneous & 50 & $0^{o}$& 13293.06 &49939.53\\ 
Homogeneous & 50 & $45^{o}$& 13291.04 &50001.59\\ 
Homogeneous & 50 & $90^{o}$ & 13348.76 &49922.73\\ 
Homogeneous & 100 & $0^{o}$ & 15527.69 &50114.11\\ 
Homogeneous & 100 & $45^{o}$ & 15511.56 &49967.17\\ 
Homogeneous & 100 & $90^{o}$ & 15401.71 & 49833.65\\ 
Homogeneous & 200 & $0^{o}$  & 17830.85 & 50078.69\\ 
Homogeneous & 200 & $45^{o}$ & 17932.87 & 50064.42\\ 
Homogeneous & 200 & $90^{o}$ & 17830.85  & 49931.748\\ 
Homogeneous & 300 & $ 0^{o}$ & 18687.33 & 50048.33 \\ 
Homogeneous & 300 & $45^{o}$ & 18572.12& 49922.67\\ 
Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ \hline
\end{tabular}
\caption{Escape fraction for a Homogeneous Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccccc} \hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\  \hline 
Central & 50 & $0^{o}$ & 4809.881 & 49917.069 \\ 
Central & 50 & $45^{o}$ & 4829.21 & 49811.79 \\ 
Central & 50 & $90^{o}$ & 4845.108 & 49853.039\\ 
Central & 100 & $0^{o}$ & 4809.665 & 49921.30 \\  
Central & 100 & $45^{o}$ & 4828.65 & 49820.13 \\ 
Central & 100 & $90^{o}$ & 4846.45 & 49854.0 \\ 
Central & 200 & $0^{o}$  & 4809.63 & 49917.64 \\ 
Central & 200 & $45^{o}$ & 4829.25 & 49818.49 \\ 
Central & 200 & $90^{o}$ & 4844.89 & 49856.66 \\ 
Central & 300 & $ 0^{o}$ & 4810.56 & 49922.98\\ 
Central & 300 & $45^{o}$ & 4831.16 & 49823.33\\ 
Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ \hline
\end{tabular}
\caption{Escape fraction for the central Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}
